Untitled

### 2017-08-27 PaperCode.Rmd
Added Hounslow

@@

@@

DenbigshireDATA <- read_excel("FOI 2503 DenbighshireDiscountsLSOA.xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(8:9)

@@

@@

@@

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()

@@

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

@@

@@

confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)
confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)

BinomExtent <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
rpartExtent <- rpart(Reference~ Extent + price + VacantsPerc,data=ModelMe)

confusionMatrix((predict(BinomExtent, ModelMe, type = "response")>0.5) , ModelMe$Reference)
confusionMatrix(predict(rpartExtent, ModelMe, type = "prob")[,2] , ModelMe$Reference)

@@

EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

>>>>

#West Midlands Brum
```{r}

setwd(file.path(RegionsComp, "Region West Midlands"))

SandWellDATA <- read_excel("FOI - SandwellDiscountsLSOA - FS57000079 Disc.xlsx" )[1:4] %>%  
  StructureData(2:6)

WolverhamptonDATA <- read_excel("WolverhamptonDiscountsLSOA.XLSX"  )[1:4] %>%  
  StructureData(c(2:5,7))

WalsallDATA <- read_excel("WalsallDiscountsLSOA.XLSX" )[1:4] %>%  
  StructureData(c(4:5,7:8))

@@

KirkleesDATA <- read_excel("Jonathan Bourne KirkleesDiscountsLSOA Complete.xlsx" )[1:4] %>%
  StructureData(2:5)

@@

DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(c(8:9,11,13))

@@

unaffordLAD <- unafford %>%
  rename(LAD11CD = Local.authority.code) %>%
  group_by(LAD11CD) %>%
  mutate(TotInc = Yearly.income*Pop) %>%
  summarise(TotInc = sum(TotInc),
            Pop = sum(Pop)) %>%
  mutate(meanInc = TotInc/Pop)

@@

#Used when elements need to be deleted and reloaded
#saveRDS(BootStrapRESExO, "BootStrapRESExO.rds")

@@

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valuerat HounslowLONDATA <- read_excel("Hounslow Discounts - Bourne Info -210817.xls" )io>1)) + geom_point()

@@

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
  left_join(Rural, by = "LAD11CD") %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

@@

  model <- rpart(Reference~ Extent + 
                   price + 
                   VacantsPerc  
                 ,data=as.data.frame(TestResample))

@@

confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)  
confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)

ModelMe %>% 
  mutate(Outcome = as.logical(MultiCheck$Outcome)) %>%
  filter(Outcome != Reference) %>%
  select(LAD, Outcome, Reference)

@@

EnglandCompTab <- EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

EnglandCompTab

xtable(EnglandCompTab, caption="Summary of effecrt across England",
       label = "tab:EnglandCompTab") %>% 
  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))
